%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout
\usepackage{fontawesome}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Tomáš Heřman} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf \faicon{map-marker} Address} \>Prague,\\ % Address line 1
\> Czech Republic \\ % Address line 2
{\bf \faicon{birthday-cake} Date of Birth} \> 21$^{st}$ February 1989 \\ % Date of birth 
{\bf \faicon{flag} Nationality} \> Czech % Nationality
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf \faicon{phone} Phone} \> +420 728 466 416 \\ % Mobile phone
{\bf \faicon{envelope} Email} \> \href{mailto:tomas.herman@gmail.com}{tomas.herman@gmail.com} \\ % Email address
{\bf \faicon{github} GitHub} \> \href{https://github.com/tomasherman}{github.com/tomasherman}
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Open source}
\opensource{\href{https://github.com/avast/datadog4s}{datadog4s}}{Library for easy monitoring of cats-effect based Scala 
applications with \href{https://www.datadoghq.com/}{Datadog}. Developed for Avast but maintained, designed and developed mostly by me.}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{Aug 2019 -}{Present}
{Avast Software, Prague}
{http://www.avast.com}
{Team Lead, Senior Software engineer}
{Promoted to the position of Team lead of 3 (and later 6) backend-developers. In addition to Team Lead duties (1 on 1s, Sprint plannings etc), I also spend a lot of time
talking to Product about new features, improvements and ideas. I help design said features and make sure they get implemented on time and in adequate quality. I take care about make sure that
estimates are realistic and what we commit to is feasible and relevant. \\

\jobtechnologies{Scala, Cassandra, Kafka, RabbitMQ, Netty, Http4s, cats-effect, Netty, Kubernetes, Helm, AWS, Terraform}}

%------------------------------------------------

\job
{Mar 2016 -}{Aug 2019}
{Avast Software, Prague}
{http://www.avast.com}
{Software Engineer}
{As a Software Engineer I worked on many different services, all related to providing/processing data to/from Avast Anti Virus. In addition to coding,
i played a big role in introducing Functional Programming to engineers that were already working in \emph{Scala as a better Java} mode. \\
To do that, I (with few others) prepared many talks, libraries etc to introduce FP concepts/techniques to my colleagues. Some interesting projects I worked on:
\begin{itemize}
    \item DNS proxy written in Netty
    \item System for scanning Android APKs from 3rd parties
    \item High throughput, highly cost-sensitive websocket server for \href{https://www.avast.com/en-us/omni}{Omni project}
\end{itemize}

In addition to SW Engineer workload I've been a L1 on-call support for automated tests and monitors.

\jobtechnologies{See Above}}

%------------------------------------------------

\job
{2014 -}{Feb 2016}
{Golem Trading for Wikidi, Prague, Czech Republic}
{https://www.golemtrader.com/}
{Software engineer}
{I returned to Wikidi to work in a very small team on Golem trading platform. I worked on \emph{Trader} app which made decision about trading and i also written a UI for the founder/thought leader to watch/control what the trader is doing. Eventually I became the lead for the platform. Eventually we moved to cryptocurrencies.\\
\jobtechnologies{Java, Kotlin, \href{https://en.wikipedia.org/wiki/Financial_Information_eXchange}{FIX}, ReactJS, Google Sheets updated by Python}}

%------------------------------------------------

\job
{2013 -}{2014 }
{Spinoco, Prague, Czech Republic}
{https://www.spinoco.com/}
{Solution Designer}
{Worked as a full-stack developer in a small team on a Telco app, which used very advanced Scala concepts/tools like scalaz-streams or ScalaJS. In addition to developer work I also had a chance to inteact with clients and even been on a sales meeting.\\
\jobtechnologies{Scala(JS), Scalaz Streams (later evolved into FS2 streams), Scalaz, Play Framework, Cassandra}}

%------------------------------------------------

\job
{2012 -}{2013}
{Magic Table project for Wikidi, Prague, Czech Republic}
{https://www.magictable.com}
{Developer}
{I was the sole developer on the project (lead by \href{https://michal.illich.cz/}{the founder}). I was responsible for web-crawling, data processing pipeline, applying machine learning libraries and basically everything else. \\
\jobtechnologies{Python, R}}

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
\bf{2008-2012} \> BCs. in Intelligent systems - \href{https://www.cvut.cz/}{Czech Technical University, Prague} \\[5pt]
    \> As a final project I wrote Minecraft server in Scala and Akka 
}

%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Software Engineering Skills}

\skillgroup{Programming Languages}
{
\textit{Scala} - Lot of experience with typelevel stack (http4s, cats-effect, etc)\\
\textit{Python} - Used in past and for ad-hoc scripts etc\\
\textit{Java} - Used in past\\
}

%------------------------------------------------

\skillgroup{Operations and Cloud}
{
\textit{Kubernetes, Helm} - maintenance and development of helm/kubernetes services\\
\textit{AWS, Terraform, Spinnaker} - user level experience\\
\textit{Grafana, Datadog, Icinga, VictorOps} - used to make sure the code behaves as it should \\
}

\skillgroup{Others}
{
\textit{Git, Bash} \\
\textit{Cassandra, Kafka, RabbitMQ}
}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\interestsgroup{
\interest{Running, hiking, weight-lifting}
\interest{Rock climbing - teaching and practicing}
\interest{Investing and finance}
}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}
\interestsgroup{
\interest{Czech - native}
\interest{English - very good, successfully used in business setting}
}


%----------------------------------------------------------------------------------------
%	OTHER SECTION
%----------------------------------------------------------------------------------------

\section{Others}
\skillgroup{Rock Climbing instructor}
{
\textit{Rock/Sport climbing instructor qualification by \href{https://www.horosvaz.cz/}{Czech Rockclimbing association}}\\
\textit{3 years of teaching rock-climbing to beginners as a hobby}
}

%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------

% \section{Referees}
% 
% \parbox{0.5\textwidth}{ % First block
% \begin{tabbing}
% \hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
% {\bf Name} \> Bill Lumbergh \\ % Referee name
% {\bf Company} \> Initech Inc. \\ % Referee company
% {\bf Position} \> Vice President \\ % Referee job title 
% {\bf Contact} \> \href{mailto:bill@initech.com}{bill@initech.com} % Referee contact information
% \end{tabbing}}
% \hfill % Horizontal space between the two blocks
% \parbox{0.5\textwidth}{ % Second block
% \begin{tabbing}
% \hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
% {\bf Name} \> Michael "Big Mike" Tucker\\ % Referee name
% {\bf Company} \> Burbank Buy More \\ % Referee company
% {\bf Position} \> Store Manager \\ % Referee job title 
% {\bf Contact} \> \href{mailto:mike@buymore.com}{mike@buymore.com} % Referee contact information
% \end{tabbing}}
% 
% %----------------------------------------------------------------------------------------
% 
\end{document}